\documentclass[a4paper,10pt]{article}
%-----------------------------------------------------------
\usepackage[top=0.75in, bottom=0.75in, left=0.55in, right=0.85in]{geometry}
\usepackage{graphicx}
\usepackage{url}
\usepackage{hyperref}
\usepackage{palatino}
\usepackage{tabularx}
\fontfamily{SansSerif}
% http://ctan.org/pkg/enumitem
\usepackage{enumitem}
\selectfont

\usepackage[T1]{fontenc}
\usepackage
%[ansinew]
[utf8]
{inputenc}

\graphicspath{ {/} }

\usepackage{color}
\definecolor{mygrey}{gray}{0.75}
\textheight=9.75in
\raggedbottom

\setlength{\tabcolsep}{0in}
\newcommand{\isep}{-2 pt}
\newcommand{\lsep}{-0.5cm}
\newcommand{\psep}{-0.6cm}
\renewcommand{\labelitemii}{$\circ$}

\pagestyle{empty}
%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}

\newcommand{\resheading}[1]
{{
	\small \colorbox{mygrey}
	{\begin{minipage}
		{1.0\textwidth}
		{\textbf{#1 \vphantom{p\^{E}}}}
	\end{minipage}}
}}

\newcommand{\ressubheading}[3]
{
	\begin{tabular*}
		{12.62in}
		{l @{\extracolsep{\fill}} r}
    	\textsc{{\textbf{#1}}} & \textsc{\textit{[#2]}}
    	\\
	\end{tabular*}
	\vspace{-8pt}
}
%-----------------------------------------------------------

\begin{document}
	\begin{center}
		\begin{Large}
			{C A N D I D A T E\ \ \ N A M E} 
		\end{Large} 
		\\
		DTU/2KXX/XX/XXX
	\end{center}
	\indent \hspace{10pt} mail-id@mail.com \hspace{300pt} +91-XXXXXXXXXX 
	\\[-0.3cm]

	\resheading{\textbf{ACADEMIC DETAILS} }
	\\[\lsep]

	%\begin{table}[ht!]
	\begin{center}
		\indent 
		\begin{tabular}
			{ l @{\hskip 0.15in} l @{\hskip 0.25in} l @{\hskip 0.25in}  l }
			\hline
			\textbf{Year} & \textbf{Degree / Examination} & \textbf{Institute} & \textbf{GPA / \%} \\
			\hline
			201X-Present & B.Tech in \_\_\_\_\_\_\_\_ Engineering & 
			Delhi Technological University, Delhi & X.XX\\
			201X & AISSCE/ICSE (XII) & 
			School Name, City & XX.X\% \\
			2013 & AISSE/ICSE (X) & 
			School Name, City & XX.X\\
			\hline
		\end{tabular}
	\end{center}
%\end{table}

	\resheading{\textbf{WORK EXPERIENCE} }\\[\lsep]
	\\[-0.25cm]
	\begin{itemize}
		\item \textbf{Company X |  Summer Intern} \hspace{235pt} \emph{(May 20XX - Aug 20XX)}
 		\\ [0.1cm]
 		\emph{(Project: \textbf{Project Name}, Mentor: ----------)} \\[-0.6cm]
    		\begin{itemize}\itemsep \isep
				\item What key role you played.
   				\item What was the impact of this role. 
    			\item What other role did you played.
    			\item What was the impact of this role.
    			\item \underline{\textbf{Technologies Used:}} 
    		\end{itemize}
	\end{itemize}

	\resheading{\textbf{ACADEMIC PROJECTS} }\\ [-0.45cm]
	\begin{itemize}
	
		\item \textbf{Project Name}\\[\lsep]
		\begin{itemize}[noitemsep,topsep=0pt]
			\item Brief description of the project; What was your role if multi-member team. 
			\item What was the end result of doing this project.
		\end{itemize}

		\item \textbf{Project Name}\\[\lsep]
		\begin{itemize}[noitemsep,topsep=0pt]
			\item Brief description of the project; What was your role if multi-member team. 
			\item What was the end result of doing this project.
		\end{itemize}
	
	\end{itemize}

	\resheading{\textbf{SKILLS} }\\[-0.3cm]
	\begin{itemize}
		\item \noindent \textbf{Something} Item1, Item2,...\\
		\textbf{Something} Item1, Item2,... .
	\end{itemize}

	\resheading{\textbf{ACADEMIC ACHIEVEMENTS AND AWARDS} }\\[-0.4cm]
	\\ \\
	\indent 
	\begin{tabular}
		{ l @{\hskip 0.15in} l @{\hskip 0.15in} l @{\hskip 0.15in} l @{\hskip 0.15in} l }
		20XX         & {Achievement}  & Domain.\\
		20XX         & {Achievement}  & Domain.\\
		20XX         & {Achievement}  & Domain.\\
		20XX         & {Achievement}  & Domain.\\
		20XX         & {Achievement}  & Domain.\\
	\end{tabular}

	\resheading{\textbf{POSITIONS OF RESPONSIBILITY} }\\[-0.4cm]
	\begin{itemize}
		\item As Coordinator (Event X) for ABC Year X- all India inter-collegiate cultural festival\\[\lsep]
		\begin{itemize}[noitemsep,topsep=0pt]
			\item What was your role in this position 
			\item Did you achieve any recognition for your role.
		\end{itemize}
		
		\item XYZ, the student post of the resident/ society (n+ inmates)\\[\lsep]
		\begin{itemize}[noitemsep,topsep=0pt]
			\item What was your role in this position 
			\item Did you achieve any recognition for your role.
		\end{itemize}

	\end{itemize}


	\resheading{\textbf{EXTRA-CURRICULAR ACTIVITIES AND ACHIEVEMENTS} }\\[-0.4cm]
	\indent 
	
	\begin{itemize}[noitemsep]
		\item \noindent Won X ; X awards in X club / society, year X
		\item \noindent Member of XYZ sports team for College / resident and won X medal in X tournament, year X
		\item \noindent Other free time interests.
	\end{itemize}
	
	\resheading{\textbf{OTHER INFORMATION} }\\[-0.4cm]
	\begin{itemize}
		\item \noindent Other Information
	\end{itemize}

	\resheading{\textbf{DECLARATION} }\\[-0.5cm]
	\begin{itemize}
		\item \noindent I hereby declare that the details furnished above are true and correct to the best of my knowledge and belief.
	\end{itemize}

\end{document}


